A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-02 paper.tex

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to brokers while ensuring the privacy. The details would be further illustrated in Section.\ref{section:ta_endpoint}.

\section{Masked Authenticate Messaging}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

MAM publishes authenticated streaming data as zero-value transactions to the Tangle and provides the ability to publish and fetch encrypted messages over the network along with data integrity and access control. With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage. Channel and endpoint represent a stream of messages, which functions as singly-linked lists. The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point. Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID. A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint. The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.

A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint. This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.

\begin{figure}[h]
    \centering
    \includegraphics[width=2.5in]{mam_struct}
    \caption{The concept of MAM.}
    \label{fig:mam_struct}
\end{figure}

The authentication in MAM includes two aspects: source and data. Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender. These are achieved through the MSS which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions. However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start. Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data. Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.

%scalability
The importance of scalable key and data entry points management increases as the service operating over time. In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data. Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems. Assuming the length of data stream is 7, and each record is encrypted with the same key. With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.

@@

%classify
The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages. For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs. Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entry points of the data steams should be reserved.

%data trace
Moreover, data traceability is an important security issue that allows users to track the changes of data. Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity. Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions. MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace. In this paper, we evaluate the performance of MAM, and improve the efficiency with different strategies. Also, we take offloading the computation tasks to brokers as another possible approach for IoT devices, since brokers are considered to have higher computational power.

\subsection{TA - endpoint}
\label{section:ta_endpoint}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy. The details would be further illustrated in Section.\ref{section:ta_endpoint}.

\section{Masked Authenticate Messaging}
MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle. The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only. With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

\subsection{The Message Streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel ID = root$ i.e., the MSS Merkle root. Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point.

The publishers can decide whether to turn the encryption on and off to protect messages. If the message payload is encrypted, subscribers are required for encryption keys to decode messages. For validation check, subscribers can validate the signature added in the signature section of MAM bundle.

\subsection{Enable Access Control and Authentication}
The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels. The authentication in MAM includes two aspects: source and data. Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender. These are achieved through the MSS and One-way hash functions. However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start. Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.

\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
%scalability
\subsubsection{A Scalable Keys and Data Entry Points Management}
The importance of scalable key and data entry points management increases over time. In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data. Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems. Assuming the length of data stream is 7, and each record is encrypted with the same key. With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.

@@

%classify
\subsubsection{Data Sreams Classification}
The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages. For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs. Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. To do the classification in other distributed storage also encounters the aforementioned scalability problem.

%data trace
\subsubsection{A Traceable Data Stream}
Data tracability is an important security issue that allows users to track the changes of data. Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity. Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions. MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

\subsection{Delegate MAM operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cyptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers.
